Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-11-10 paper/main.tex
Added description of NIST and SuperCop APIs

\begin{acronym}
\acro{AES}{Advanced Encryption Standard}
\acro{CEB}{Capability Extension Block}
\acro{FEC}{Forward Error Correction}
\acro{LAFS}{Least-Authority Filesystem}
\acro{NIST}{National Institute of Standards and Technology}
\acro{RAM}{Random Access Memory}
\acro{RAID}{Redundant Array of Independent Disks}
\acro{SHA}{Secure Hash Algorithm}
\acro{SSE2}{Streaming SIMD Extensions 2}
\acro{SSSE3}{Supplemental Streaming SIMD Extensions 3}
\acro{SUPERCOP}{System for Unified Performance Evaluation Related to
Cryptographic Operations and Primitives}
\acro{UEB}{URI Extension Block}
\end{acronym}

@@

@@

The Round 2 \ac{SHA}-3 candidates are all included in the toolkit, with a number
of different optimizations for each candidate. Optimizations range from
32-/64-bit specific implementations, the use of extended instruction sets such
as \ac{SSE2} and \ac{SSE3}, optimizations for different number of cores and
others. The toolkit will also try different compiler optimizations to get the
best results possible for each function.
% TODO: Insert image to visualize the forest of different implementations.

@@

@@

>>>>

\begin{acronym}
\acro{AES}{Advanced Encryption Standard}
\acro{API}{Application programming interface}
\acro{CEB}{Capability Extension Block}
\acro{FEC}{Forward Error Correction}
\acro{LAFS}{Least-Authority Filesystem}
\acro{NIST}{National Institute of Standards and Technology}
\acro{RAM}{Random Access Memory}
\acro{RAID}{Redundant Array of Independent Disks}
\acro{SHA}{Secure Hash Algorithm}
\acro{SSE2}{Streaming SIMD Extensions 2}
\acro{SSSE3}{Supplemental Streaming SIMD Extensions 3}
\acro{SUPERCOP}{System for Unified Performance Evaluation Related to
Cryptographic Operations and Primitives}
\acro{UEB}{URI Extension Block}
\end{acronym}

@@

\subsubsection{\ac{NIST} \ac{SHA}-3 \ac{API}}
\ac{NIST} required that every submission conform to a specified
\ac{API}\cite{s_fedreg}. The \ac{API} is specified at \cite{s_nistapi} and in
shortness it requires every candidate to implement four functions.

\begin{verbatim}
HashReturn Init(hashState *state, int hashbitlen);
HashReturn Update(hashState *state, const BitSequence *data, 
    DataLength databitlen);
HashReturn Final(hashState *state, BitSequence *hashval);
HashReturn Hash(int hashbitlen, const BitSequence *data, 
    DataLength databitlen, BitSequence *hashval);
\end{verbatim}

The Init() function basically sets up the internal state of the function, to
make it ready to start processing real data. The Update() function is used to
provide the actuall data to the hash function. The Final() function should be
called when all necessary data has been gived through Update(), it will then
finish the hash function and provide the digest. The Hash() function basically a wrapper
for doing a call to the three other functions.

HashReturn is an enum representing that an operation either succeded (0) or
went wrong. The BitSequence is a representation of an array of bytefields and
DataLength represents the size in bits of the data provided.

@@

The Round 2 \ac{SHA}-3 candidates are all included in the toolkit, with a number
of different optimizations for each candidate. Optimizations range from
32-/64-bit specific implementations, the use of extended instruction sets such
as \ac{SSE2} and \ac{SSSE3}, optimizations for different number of cores and
others. The toolkit will also try different compiler optimizations to get the
best results possible for each function.
% TODO: Insert image to visualize the forest of different implementations.

@@

\subsubsection{\ac{SUPERCOP} \ac{API}}
\ac{SUPERCOP} specifies an \ac{API} which all submitted implementations must
conform to\cite{s_supercopapi}. This \ac{API} specifies the naming and
organization of files, and that a submission must include a function
crypto\_hash() which is similar to the function Hash() in the \ac{NIST} \ac{SHA}-3
\ac{API}. The only difference beeing the naming of datatypes and that the
crypto\_hash() function does not need an input of how long the output of the
hash function should be. Instead double or different submissions are used for
different output lengths.

\begin{verbatim}
int crypto_hash(unsigned char *out, const unsigned char *in,
    unsigned long long inlen)
\end{verbatim}

@@

\input{tables/supercop_long_msgs}
\input{tables/supercop_4096}
\input{tables/supercop_1536}
\input{tables/supercop_576}
\input{tables/supercop_64}
\input{tables/supercop_8}
